The \project{unRAVE} catalog

### 2016-09-05 article/unrave.tex
Additions to tex, plot_clusters.py, and padova isochrones, added cluster HRDs

After verifying that our stellar labels are comparable with other
high-resolution studies, here we verify that the abundances we find
are consistent with expectations from astrophysics.  One example is stars in
globular clusters, which show anti-correlations in light element abundances 
\citep[e.g.,][and references therein]{Norris_Da_Costa_1995,Carretta_2009}.  In the \rave\
survey, \cite{Anguiano_2015} found 70 stars with positions and radial velocities that are
consistent with being members of globular clusters: 49 stars belonging to NGC~5139 ($\omega$~Centauri), 11 members of the retrograde
globular cluster NGC~3201, and 10 members of NGC~362.  
All of these systems are well-studied and exhibit abundance anti-correlations 
in Na--O and Mg--Al \citep{Marino_2011,Carretta_2009,Carretta_2013,Munoz_2013}.  Other correlations are also present 
(e.g., C--N), but those relationships are less relevant for this work because 
we do not measure C and N abundances here.  We note that \emph{none} of these 
globular cluster stars were present in our training set.

@@

% Some literature notes:
% See http://iopscience.iop.org/article/10.1088/0004-637X/731/1/64/pdf
% NGC 3201 has Na-O anti-correlation: Carretta et al. (2009)
% NGC 362 has "two discrete groups along the Na-O anti-correlation": https://arxiv.org/abs/1307.4085
% NGC 362 has Mg-Al relationship (low Mg scatter, large Al scatter) --> Carretta (2013)
% NGC 362 has a large metallicity spread in RAVE (Anguiano_2015) but not the case in high-res studies (e.g. https://arxiv.org/abs/1307.4085 has a metallicity spread of 0.05/0.08 dex) may indicate better cluster selection needed and can be done with cannon results.
% NGC 3201 has Mg-Al relationship (http://arxiv.org/pdf/1305.3645.pdf and references therein)

\subsubsection{Open clusters}
\label{sec:open-cluster-validation}

@@

>>>>

After verifying that our stellar labels are comparable with other
high-resolution studies, here we verify that the abundances we find
are consistent with expectations from astrophysics.  One example is stars in
globular clusters, which show anti-correlations in light element abundances 
\citep[e.g.,][and references therein]{Norris_Da_Costa_1995,Carretta_2009}.  In the \rave\
survey, \cite{Anguiano_2015} found 70 stars with positions and radial velocities that are
consistent with being members of globular clusters: 49 stars belonging to NGC~5139 ($\omega$~Centauri), 11 members of the retrograde globular cluster NGC~3201, and 10 members of NGC~362. In addition to these systems, NGC~6752 and 47~Tuc were observed \citep{Kunder_2016}. In the top panel of Figure~\ref{fig:globular-cluster-HRD} we plot the spectroscopic H-R diagram for the members of these globular clusters. For comparison, in the bottom panel of Figure~\ref{fig:globular-cluster-HRD} we show the same as the top panel but for the RAVE DR4. For a detailed description of the cluster membership for NGC~5139, NGC~3201, and NGC~362 we refer the reader to \cite{Anguiano_2015}. The membership selection of the remaining clusters can be found in \cite{Kunder_2016}. \stub{check if this is the case in Kunder et al 2016.}

All of these systems (\stub{check if this is the case for the remaining two new GCs added.}) in \cite{Anguiano_2015} are well-studied and exhibit abundance anti-correlations 
in Na--O and Mg--Al \citep{Marino_2011,Carretta_2009,Carretta_2013,Munoz_2013}.  Other correlations are also present 
(e.g., C--N), but those relationships are less relevant for this work because 
we do not measure C and N abundances here.  We note that \emph{none} of these 
globular cluster stars were present in our training set.

@@

% Some literature notes:
%check if NGC 6571 has anticorrelations present
% See http://iopscience.iop.org/article/10.1088/0004-637X/731/1/64/pdf
% NGC 3201 has Na-O anti-correlation: Carretta et al. (2009)
% NGC 362 has "two discrete groups along the Na-O anti-correlation": https://arxiv.org/abs/1307.4085
% NGC 362 has Mg-Al relationship (low Mg scatter, large Al scatter) --> Carretta (2013)
% NGC 362 has a large metallicity spread in RAVE (Anguiano_2015) but not the case in high-res studies (e.g. https://arxiv.org/abs/1307.4085 has a metallicity spread of 0.05/0.08 dex) may indicate better cluster selection needed and can be done with cannon results.
% NGC 3201 has Mg-Al relationship (http://arxiv.org/pdf/1305.3645.pdf and references therein)

\subsubsection{Open clusters}
\label{sec:open-cluster-validation}
The RAVE survey has observed several open clusters which can serve as a qualitative sanity check that the stellar parameters match our expectations. These include .... \stub{add more here about each open cluster plus its members}. The membership selection of the remaining clusters can be found in \cite{Kunder_2016}. \stub{check if this is the case in Kunder et al 2016.}

 In Figure~\ref{fig:globular-cluster-HRD}, we plot the cannon-derived H-R diagram (top panel) and compare it to the RAVE DR4 H-R diagram (bottom panel) for the stars which are probably members of the open clusters.

@@

\begin{figure*}[p]
\includegraphics[width=\textwidth]{figures/HRD_GCs.pdf}
\caption{Top Panel: Cannon-derived $\logg$ as a function of $\teff$ for globular cluster members. The cluster name is indicated in the top left corner. The points are color-coded by the metallicity of the member star. Bottom Panel: RAVE DR4 $\logg$ as a function of $\teff$ for the same clusters in the top panel. The points are color-coded by the metallicity of the member star. In both panels, the black line represent the theoretical expectation of a single stellar population from the Padova isochrone set. \label{fig:globular-cluster-HRD}}
\end{figure*}

\begin{figure*}[p]
\includegraphics[width=\textwidth]{figures/HRD_OCs.pdf}
\caption{Same as Figure~\ref{fig:globular-cluster-HRD} for the open cluster members in the RAVE dataset.  \label{fig:open-cluster-HRD}}
\end{figure*}
